\vspace{-\baselineskip} Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3.2\baselineskip}

### 2017-03-27 paper/ms.tex
bumping version number, figures for julia tutorial, publish script
adding Zenodo DOI to ms

In the following pages, we motivate the general problem of GP regression,
describe the previously published scalable method \citep{Rybicki:1995,
Ambikasaran:2015} and our generalization, and demonstrate the model's
application on various real and simulated data sets.
Alongside this paper, we have released well-tested and documented open source
implementations written in \project{C++}, \project{Python}, and
\project{Julia}.
These are available online at \project{GitHub}
\url{https://github.com/dfm/celerite} and \project{Zenodo} \dfmtodo{add zenodo
archive}.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/astero-11615890-comparisons.pdf}
\caption{A comparison between the Lomb-Scargle estimator of the PSD and the
posterior inference of the PSD as a mixture of stochastically-driven simple
harmonic oscillators.
(top) The periodogram of the \kepler\ light curve for KIC~11615890 computed
    on the full four year baseline of the mission.
(middle) The same periodogram computed using about a month of data.
(bottom) The power spectrum inferred using the mixture of SHOs model described
    in the text and only one month of \kepler\ data.
    The black line shows the median of posterior PSD and the gray contours
    show the 68\% credible region.
    \figurelabel{astero}}
\end{center}
\end{figure}

@@

Alongside this paper, we have released a well-tested and documented open
source software package that implements the method and all of the examples
discussed in these pages.
This software is available at \url{https://github.com/dfm/celerite}\footnote{%
This version of the paper was generated with git commit \texttt{\githash}
(\gitdate).} and it is made available under the MIT license.

>>>>

In the following pages, we motivate the general problem of GP regression,
describe the previously published scalable method \citep{Rybicki:1995,
Ambikasaran:2015} and our generalization, and demonstrate the model's
application on various real and simulated data sets.
Alongside this paper, we have released well-tested and documented open source
implementations written in \project{C++}, \project{Python}, and
\project{Julia}.
These are available online at \project{GitHub}
\url{https://github.com/dfm/celerite} and \project{Zenodo}
\citep{Foreman-Mackey:2017}.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{figures/astero-11615890-comparisons.pdf}
\caption{A comparison between the Lomb-Scargle estimator of the PSD and the
posterior inference of the PSD as a mixture of stochastically-driven simple
harmonic oscillators.
(top) The periodogram of the \kepler\ light curve for KIC~11615890 computed
    on the full four year baseline of the mission. The orange line shows a
    smoothed periodogram and the blue line indicates the level of the
    measurement uncertainties.
(middle) The same periodogram computed using about a month of data.
(bottom) The power spectrum inferred using the mixture of SHOs model described
    in the text and only one month of \kepler\ data.
    The black line shows the median of posterior PSD and the gray contours
    show the 68\% credible region.
    \figurelabel{astero}}
\end{center}
\end{figure}

@@

Alongside this paper, we have released a well-tested and documented open
source software package that implements the method and all of the examples
discussed in these pages.
This software is available on GitHub
\url{https://github.com/dfm/celerite}\footnote{% This version of the paper was
generated with git commit \texttt{\githash} (\gitdate).} and Zenodo
\citep{Foreman-Mackey:2017}, and it is made available under the MIT license.
